---
title: "Case Study 2"
author: "Akshay Vellore, Irith Chaturvedi, Aryaman Kushwaha, Pranav Pullabhotla"
date: "2024-12-07"
output:
  pdf_document: default
  html_document: default
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## INTRODUCTION

For this case study, we aim to analyze the alcohol percentage in wine by
examining its relationship with various chemical components and
characteristics. We will explore how factors such as fixed acidity,
volatile acidity, citric acid, residual sugar, chlorides, free sulfur
dioxide, total sulfur dioxide, density, pH, sulfates, and wine type
influence the alcohol content of wine. By understanding these
relationships, we can gain insights into the factors that contribute to
variations in alcohol percentage. We are using a significance level of
0.05.

**Read the data**

```{r}
wines = read.csv('wines.csv')
head(wines)
```

## Exploratory Data Analysis

a)  Dimensions of our dataset

```{r}
dim(wines)
```

b)  Histogram for the Alcohol percentage for Wines

```{r}
hist(wines$alcohol, xlab = "Alcohol Pecentage", 
     main = "Histogram for the Alcohol percentage for Wines")
```

c)  Box PLot for Alcohol Percentage

```{r}
boxplot(x = wines$alcohol, ylab = "Alcohol Pecentage", 
     main = "Box Plot for the Alcohol percentage in Wines")
```

d)  Number of missing values (if any) per column

```{r}
colSums(is.na(wines))
```

e)  Correlation matrix

```{r}
wines_cont = wines[, -c(12)]
cor(wines_cont)
```

There is one notable pair of highly correlated variables: free sulphur 
dioxide content and total sulphur dioxide (0.72)

f)  Scatter plots to visualize highly correlated variables

```{r}
par(mfrow = c(1, 2))
plot(x = wines$free.sulfur.dioxide, wines$total.sulfur.dioxide, 
     ylab = "total sulfur dioxide Percentage", 
     xlab = "free sulfur dioxide Percentage")
```

The scatter plot do show some correlation for our variables. It would
be interesting to explore their relationships further in our report.

g)  Some summary statistics for the Alcohol content:

```{r}
summary(wines$alcohol)
```

Minimum alcohol percent for a wine in the dataset = 8% Mean alcohol
percent for a wine in the dataset = 10.49% Maximum alcohol percent for a
wine in the dataset = 14.9%

```{r}
wines[which(wines$alcohol == max(wines$alcohol)), ]
```

## Linear Model Development

We will create a 80-20 train and test split on our data.

```{r}
set.seed(2345)
train = sample(1:nrow(wines), 0.8*nrow(wines))
train.df = wines[train,]
test.df = wines[-train,]
dim(train.df)
dim(test.df)
```

Training and Testing Error for the full model

```{r}
wines.training = lm(alcohol~. , train.df)
rmse = function(x, y) {
  sqrt(mean((x-y)^2))
}
rmse(fitted(wines.training), train.df$alcohol)
```

```{r}
rmse(predict(wines.training, test.df), test.df$alcohol)
```

This is the RMSE for the training and testing data using the full model

train RMSE = 0.51558 test RMSE = 0.45287

a)  Greedy Algorithms for Model selection using information criteria

Greedy Algorithm using **AIC** for model selection

```{r}
step(lm(alcohol ~., data = train.df), direction = "both")
```

According to the AIC criteria for model selection:

The ideal model with the lowest AIC is:

alcohol \~ fixed.acidity + volatile.acidity + citric.acid +
residual.sugar + chlorides + free.sulfur.dioxide + density + pH +
sulphates + type

Greedy Algorithm using **BIC** for model selection

```{r}
n = nrow(train.df)
step(lm(alcohol~., data = train.df), direction = "both", k = log(n))
```

The ideal model calculated using BIC critera is the same as calculated
using the AIC criteria, i.e:

alcohol \~ fixed.acidity + volatile.acidity + citric.acid +
residual.sugar + chlorides + free.sulfur.dioxide + density + pH +
sulphates + type

Calculating the RMSE for the training and testing data using the model
selected from the Greedy Algorithm.

```{r}
wines.training_greedy = lm(alcohol ~ fixed.acidity + volatile.acidity + 
    citric.acid + residual.sugar + chlorides + free.sulfur.dioxide + density + 
    pH + sulphates + type, train.df)

rmse(fitted(wines.training_greedy), train.df$alcohol)
```

```{r}
rmse(predict(wines.training_greedy, test.df), test.df$alcohol)
```

This is the RMSE for the training and testing data using the model
chosen with greedy algorithms

train RMSE = 0.5156707 test RMSE = 0.4527027

(b) Leap-and-bounds algorithm using at least 3 different criteria.

```{r}
library(leaps)
```

```{r}
regsubsets_selection = regsubsets(alcohol~., data = train.df)
```

```{r}
rs = summary(regsubsets_selection)
```

```{r}
rs$which
```

Adjusted-R\^2 - The best model is the one with the largest Adjusted R\^2

```{r}
rs$adjr2
```

Using Adjusted R\^2 values, the ideal model is Model 8 - Adj R\^2 =
0.8074568

alcohol \~ fixed.acidity + volatile.acidity + citric.acid +
residual.sugar + density + pH + sulphates + type

CP Mallows - The best model is the one with the lowest Cp value

```{r}
rs$cp
```

Using Cp mallows, the ideal model is Model 8 - Cp = 81.62912

alcohol \~ fixed.acidity + volatile.acidity + citric.acid +
residual.sugar + density + pH + sulphates + type

BIC - The best model is the one with the lowest BIC value

```{r}
rs$bic
```

Using the BIC, the ideal model is Model 8 - BIC = -8492.725

alcohol \~ fixed.acidity + volatile.acidity + citric.acid +
residual.sugar + density + pH + sulphates + type

All three criterias state that the model 8 is the best model when using
the Leaps and Bounds algorithm.

Using the RMSE for the training and testing data using the Model 8

```{r}
wines.training_l_and_b = lm(alcohol ~ fixed.acidity + volatile.acidity + 
    citric.acid + residual.sugar + density + pH + sulphates + type, train.df)

rmse(fitted(wines.training_l_and_b), train.df$alcohol)
```

```{r}
rmse(predict(wines.training_l_and_b, test.df), test.df$alcohol)
```

This is the RMSE for the training and testing data using the model
chosen with Leaps and Bounds algorithm

train RMSE = 0.5193281 test RMSE = 0.4531508

c)  Principal Components Regression

```{r}
library(pls)
```

```{r}
wines.pcr = pcr(alcohol~., data = train.df, scale = TRUE, ncomp = 11,
                validation = "CV")
```

```{r}
summary(wines.pcr)
```

Choosing the optimal number of components using a Scree Plot:

```{r}
wines.pca = prcomp(train.df[,-c(11, 12)])
plot(wines.pca$sdev[1:11], ylab = "PCAs Std Dev", xlab = "PCA number", 
     type = "l")
```

Five PCs is a reasonable selection according to the scree plot since
this is where the PCA Standard Deviation levels out

Calculating RMSE with 5 components:

```{r}
wines_pcr_pred_5 = predict(wines.pcr, test.df, ncomp = 5)
rmse(wines_pcr_pred_5, test.df$alcohol)
```

With 5 PCs, we get a RMSE = 0.940054

But we want to select enough number of PCs to minimize RMSE, we use the
RMSEP to select PCs instead:

```{r}
set.seed(135)
pcr.mse = RMSEP(wines.pcr, newdata = test.df)
plot(pcr.mse)
```

Using the plot, the model with 11 components gives the lowest RMSEP
value.

```{r}
wines_pcr_pred = predict(wines.pcr, test.df, ncomp = 11)
rmse(wines_pcr_pred, test.df$alcohol)
```

With 11 PCs, we get a RMSE = 0.452872, which is the same as the full
model.

d)  Ridge and LASSO Regression:

**Ridge**

```{r}
library(MASS)
```

```{r}
train.df$type <- as.factor(train.df$type)
wines.ridge <- lm.ridge(alcohol ~ fixed.acidity + volatile.acidity + 
    citric.acid + total.sulfur.dioxide + residual.sugar + chlorides + 
    free.sulfur.dioxide + density + pH + sulphates, data = train.df, 
    lambda = seq(0, 1, len = 200))
summary(wines.ridge)
```

```{r}
matplot(wines.ridge$lambda, coef(wines.ridge), type="l", 
        xlab=expression(lambda), ylab=expression(hat(beta)), col=1)
which.min(wines.ridge$GCV)
abline(v = 0.165829146)
```

Our chosen lambda which is a regularization parameter that controls the
penalty applied to regression coefficients is 0.165829146

Train RMSE calculation

```{r}
wines.pred.train <- cbind(1, as.matrix(train.df[,-c(11, 12)]))
wines.pred.train <- wines.pred.train %*% coef(wines.ridge)[34,]
rmse(wines.pred.train, train.df$alcohol)
```

Train RMSE = 3.019105

Test RMSE calculation

```{r}
wines.pred.test <- cbind(1, as.matrix(test.df[,-c(11, 12)])) 
wines.pred.test <- wines.pred.test %*% coef(wines.ridge)[34,]
rmse(wines.pred.test, test.df$alcohol)
```

Test RMSE = 2.963918

Ridge Regression gave us very high RMSEs for training and testing,
indicating that it is a poor choice for this dataset.

**Lasso**

```{r}
train.y = train.df$alcohol
train.x = as.matrix(train.df[,-c(11, 12)])

library(lars)
```

```{r}
wineslasso = lars(train.x, train.y)
```

Selecting parameters using Cross Validation

```{r}
set.seed(123)
cv.ml = cv.lars(train.x, train.y)
```

```{r}
which.min(cv.ml$cv)
```

```{r}
svm<-cv.ml$index[which.min(cv.ml$cv)]
svm
```

Predicted value of the train data

```{r}
trainx<-as.matrix(train.df[,-c(11, 12)])

predlasso<-predict(wineslasso, trainx, s=svm, mode="fraction")
rmse(train.df$alcohol, predlasso$fit)
```

Predicted value of the test data

```{r}
testx<-as.matrix(test.df[,-c(11, 12)])

predlasso<-predict(wineslasso, testx, s=svm, mode="fraction")
rmse(test.df$alcohol, predlasso$fit)
```

For LASSO regression:

Train RMSE: 0.5557 Test RMSE: 0.5050

Comparing all of the different methods, we found that the greedy
algorithm with AIC and BIC gave us the model with the best (i.e. lowest)
Training and Test RMSE, and therefore it is the most optimal model out
of all the methods we tested.

**Therefore, our best linear model (based on minimizing RMSE) is:**

alcohol \~ fixed.acidity + volatile.acidity + citric.acid +
residual.sugar + chlorides + free.sulfur.dioxide + density + pH +
sulphates + type

## Model Diagnostics

**1. UNUSUAL OBSERVATIONS**

**High Leverage Points**

```{r}
wines.1 = wines.training_greedy
wines.leverages = lm.influence(wines.1)$hat
head(wines.leverages)
```

Checking for Good and bad - high leverage Points:

```{r}
library(faraway)
halfnorm(wines.leverages, nlab=6,
labs=as.character(1:length(wines.leverages)), ylab="Leverages")

```

In the plot above, we do not necessarily look for a straight line fit.
We use this plot to identify any leverages that do not follow the
pattern suggested by the rest of the data. In this case, some of the
leverages seem to be unusually large. Next, we determine which of the
leverages exceed the 2p/n threshold. p = no. of predictors for the
Model.

```{r}
wines.leverages.high =
wines.leverages[wines.leverages>2*(10/dim(wines)[1])]
length(wines.leverages.high)
```

We identify 465 High Leverage Points in our samples. next we classify
the Leverage Points as Good or Bad:

Percentage of High Leverage Points

```{r}
465/6497
```

Classifying as Good or Bad High Leverage Points:

```{r}
# Calculate the IQR for the dependent variable
IQR_y = IQR(wines$alcohol)
#Define a range with its lower limit being (Q1 - IQR) and upper limit being
#(Q3 + IQR)
QT1_y = quantile(wines$alcohol,0.25)
QT3_y = quantile(wines$alcohol,0.75)
lower_lim_y = QT1_y - IQR_y
upper_lim_y = QT3_y + IQR_y
vector_lim_y = c(lower_lim_y,upper_lim_y)
# Range for y variable
vector_lim_y

```

```{r}
wines.highlev = wines[wines.leverages>2*10/6497,]
wines.highlev_lower =
wines.highlev[wines.highlev$alcohol < vector_lim_y[1], ]
wines.highlev_upper =
wines.highlev[wines.highlev$alcohol > vector_lim_y[2], ]
wines.highlev2 = rbind(wines.highlev_lower,wines.highlev_upper)
wines.highlev2
```

**We have 27 bad High leverage Points in our dataset.**

**OUTLIERS**

Bonferroni Correction for Outlier test:

```{r}
wines.resid = rstudent(wines.1);
# Critical value WITH Bonferroni correction #
bonferroni_cv = qt(.05/(2*6497), 6497-10-1)
bonferroni_cv
```

Now we need to find out what studentized residuals exceed the Bonferroni
critical value:

```{r}
wines.resid.sorted = sort(abs(wines.resid), decreasing=TRUE)[1:10]
print(wines.resid.sorted)

```

Comparing the values against the absolute critical value from the
Bonferroni outlier test:

```{r}
wines.outliers =
wines.resid.sorted[abs(wines.resid.sorted) > abs(bonferroni_cv)]
print(wines.outliers)
```

**We have 10 outliers in our dataset**

**Influential Points**

To check for high influential points, we will use Cook’s distance with
the cooks.distance R function:

```{r}
wines.cooks = cooks.distance(wines.1)
sort(wines.cooks, decreasing = TRUE)[1:10]

```

```{r}
plot(wines.cooks)
```

**We have one influential point - data point 4381 since it's cook's
distance is greater than 1**

As point 4381 is also an outlier, we will remove it from the dataset,
since it may be causing an unusual change in behavior in our model that
is not consistent with the rest of the data. We will rerun the model on
the new dataset.

```{r}
wines_reduced = wines[-4381,]
dim(wines_reduced)
```

Creating a new model based on our reduced dataset:

```{r}
wines.1.red = lm(data = wines_reduced, alcohol ~ fixed.acidity + 
    volatile.acidity + citric.acid + residual.sugar + chlorides + 
    free.sulfur.dioxide + density + pH + sulphates + type)
summary(wines.1.red)
```

2.  **Constant variance Assumption**

The Breusch-Pagan test:

null hypothesis (Ho): the variance of error terms is constant (i.e.,
there is homoscedasticity).

Alternative Hypothesis (H1): The variance of error terms is not constant
(i.e., there is heteroscedasticity).

```{r}
library(lmtest)
bptest(wines.1.red)
```

**The variance of error terms is not constant** Based on the p-value of
the BP test = 2.2e-16 \< 0.05 -\> the p-value at the significance level,
we reject the null hypothesis and conclude that the Variance is not
constant.

Residuals vs Fitted Plot:

```{r}
plot(wines.1.red, which = 1)
```

Although the points do seem to be scattered along the zero line - almost
forming a football shaped cloud, there are some departures from the line
that are not accounted for.

To handle this, we will perform a **variance stabilizing
transformation** on our response:

We aim to find a function of the response, **h(Y)** that helps achieve
constant variance. From the above graph, we can say that the Var(Y) is
proportional to E(Y).

We will perform a square root transformation of the response:

```{r}
wines_reduced$sqrt_alcohol = sqrt(wines_reduced$alcohol)
wines.1.red_var = lm(data = wines_reduced, sqrt_alcohol ~ fixed.acidity + 
    volatile.acidity + citric.acid + residual.sugar + chlorides + 
    free.sulfur.dioxide + density + pH + sulphates + type)
summary(wines.1.red_var)
```

```{r}
bptest(wines.1.red_var)
```

Based on the p-value of the BP test = 2.2e-16 \< 0.05 -\> the p-value at
the significance level, we again reject the null hypothesis and conclude
that the Variance after transformation of the response is not constant.

A look at the Residuals vs. Fitted plot:

```{r}
plot(wines.1.red_var, which = 1)
```

The statistical BP test still fails for the transformed data, we
conclude that the transformations did not help in stabilizing and
upholding the constant variance assumption. Another approach that may 
resolve the problem is a Weighted Least Squares method. Let's use this
on top of the response transformation.

```{r}
wt <- lm(abs(wines.1.red$residuals) ~ wines.1.red$fitted.values)$fitted.values^2
wt <- 1/wt
#perform weighted least squares regression
wls_wines.1.red <- lm(alcohol ~ fixed.acidity + volatile.acidity + citric.acid +
residual.sugar + chlorides + free.sulfur.dioxide + density + pH +
sulphates + type, data = wines_reduced, weights=wt)

#view summary of model
summary(wls_wines.1.red)
```

```{r}
bptest(wls_wines.1.red)
```
It seems that even the Weighted Least Squares approach could not resolve this
issue with non-constant variance. This is a potential shortcoming of our final
model. Conclusions that are drawn from our selected model may not be reliable.

3.  **Test for Normality of Residuals**

We fist plot a histogram of the residuals for our model:

```{r}
hist(wines.1.red$residuals)

```

The residuals for the response do look like they follow a Normal
distribution, to confirm this, we can run a statistical Test for
Normality:

As we have a large number of samples in our data set, the statistical
test to check for normality in this case will be a Kolmogorov-Smirnov
test:

H0: The residuals are normally distributed (normality assumption holds)
Ha: The residuals aren't normally distributed (normality assumption
doesn't hold)

```{r}
ks.test(wines.1.red$residuals, "pnorm")
```

**The Normality assumption is not met** Based on the p-value of the KS
test = 2.2e-16 \< 0.05 -\> the p-value at the significance level, we
reject the null hypothesis and conclude that the Normality assumption
for the error terms is not met.

To handle this, we will perform a Box-Cox transformation of the
response:

```{r}
winesB.transformation = boxcox(wines.1.red,
lambda=seq(-2, 2, length=400))
best_lambda <- winesB.transformation$x[which.max(winesB.transformation$y)]
best_lambda
```

The 95% Interval for the Box-Cox plot contains ${\lambda}$s near -0.5, so we 
will perform an inverse square root transformation to try and fix the issues
with normality.

```{r}
wines_reduced$alcohol_trans = (wines_reduced$alcohol^(best_lambda) - 1)
wines_reduced$alcohol_trans = wines_reduced$alcohol_trans/(best_lambda) 
# Re-transforming the data set 
# back to the original reduced data set and performing a log transformation 

wines.1.red_norm = lm(data = wines_reduced, alcohol_trans ~ fixed.acidity + 
                       volatile.acidity + citric.acid + 
    residual.sugar + chlorides + free.sulfur.dioxide + density + 
    pH + sulphates + type)
summary(wines.1.red_norm)
```

```{r}
hist(wines.1.red_norm$residuals)

```

Although the histogram of the residuals looks more like it follows a
Normal distribution, We will look at the QQ plot for normality:

```{r}
plot(wines.1.red_norm, which = 2)
```
The QQ plot sees departures from the line.

```{r}
ks.test(wines.1.red_norm$residuals, "pnorm")
```

Based on the p-value of the KS test on the transformed response =
2.2e-16 \< 0.05 -\> the p-value at the significance level, we reject the
null hypothesis and conclude that the Normality assumption for the error
terms in our transformed model is again not met.

This is a potential shortcoming in our model (the normality assumption
not being met). This may cause our predictions to be unreliable.

4.  **Test for Collinearity**

Removing the intercept and categorical variable:

Variance Inflation Factor:

```{r}
x = model.matrix(wines.1.red)[,-c(1, 11)]
round(vif(x), dig=2)
```

Note that the standard error for the coefficient associated with
`density` is 2.133 = (4.55)\^0.5 times larger than it would have been
without collinearity.

Computing the Condition Number

```{r}
x = x - matrix(apply(x,2, mean), 6496,9, byrow=TRUE)
x = x / matrix(apply(x, 2, sd), 6496,9, byrow=TRUE)
eigenvalues.x = eigen(t(x) %*% x) 
eigenvalues.x$val
```

```{r}
sqrt(eigenvalues.x$val[1]/eigenvalues.x$val[9])
```

The condition number is 4.968, lower than 30, so we conclude that
collinearity is absent.

5.  **Tests for Linearity**

To check that all of our predictors varied linearly with the response,
we have constructed added variable plots for each predictor, as seen
below.

```{r}
# Fixed Acidity
y = update(wines.1.red, .~. -fixed.acidity)$res
x = lm(fixed.acidity ~ ., data = wines_reduced[,-c(11)])$res
plot(x, y, xlab="Fixed Acidity Residuals", ylab="Alcohol Residuals", 
     col='Darkblue', pch=3, size=3)
abline(lm(y ~ x), col='Darkblue', lwd=2)
abline(v = 0, col="red", lty=3)
abline(h = 0, col="red", lty=3)

# Volatile Acidity
y = update(wines.1.red, .~. -volatile.acidity)$res
x = lm(volatile.acidity ~ ., data = wines_reduced[,-c(11)])$res
plot(x, y, xlab="Volatile Acidity Residuals", ylab="Alcohol Residuals", 
     col='Darkblue', pch=3, size=3)
abline(lm(y ~ x), col='Darkblue', lwd=2)
abline(v = 0, col="red", lty=3)
abline(h = 0, col="red", lty=3)

# Citric Acid
y = update(wines.1.red, .~. -citric.acid)$res
x = lm(citric.acid ~ ., data = wines_reduced[,-c(11)])$res
plot(x, y, xlab="Citric Acid Residuals", ylab="Alcohol Residuals", 
     col='Darkblue', pch=3, size=3)
abline(lm(y ~ x), col='Darkblue', lwd=2)
abline(v = 0, col="red", lty=3)
abline(h = 0, col="red", lty=3)

# Residual Sugar
y = update(wines.1.red, .~. -residual.sugar)$res
x = lm(residual.sugar ~ ., data = wines_reduced[,-c(11)])$res
plot(x, y, xlab="Residual Sugar Residuals", ylab="Alcohol Residuals", 
     col='Darkblue', pch=3, size=3)
abline(lm(y ~ x), col='Darkblue', lwd=2)
abline(v = 0, col="red", lty=3)
abline(h = 0, col="red", lty=3)

# Chlorides
y = update(wines.1.red, .~. -chlorides)$res
x = lm(chlorides ~ ., data = wines_reduced[,-c(11)])$res
plot(x, y, xlab="Chlorides Residuals", ylab="Alcohol Residuals", 
     col='Darkblue', pch=3, size=3)
abline(lm(y ~ x), col='Darkblue', lwd=2)
abline(v = 0, col="red", lty=3)
abline(h = 0, col="red", lty=3)

# Free Sulfur Dioxide
y = update(wines.1.red, .~. -free.suldur.dioxide)$res
x = lm(free.sulfur.dioxide ~ ., data = wines_reduced[,-c(11)])$res
plot(x, y, xlab="Free Sulfur Dioxide Residuals", ylab="Alcohol Residuals", 
     col='Darkblue', pch=3, size=3)
abline(lm(y ~ x), col='Darkblue', lwd=2)
abline(v = 0, col="red", lty=3)
abline(h = 0, col="red", lty=3)

# Density
y = update(wines.1.red, .~. -density)$res
x = lm(density ~ ., data = wines_reduced[,-c(11)])$res
plot(x, y, xlab="Density Residuals", ylab="Alcohol Residuals", col='Darkblue', 
     pch=3, size=3)
abline(lm(y ~ x), col='Darkblue', lwd=2)
abline(v = 0, col="red", lty=3)
abline(h = 0, col="red", lty=3)

# pH
y = update(wines.1.red, .~. -pH)$res
x = lm(pH ~ ., data = wines_reduced[,-c(11)])$res
plot(x, y, xlab="pH Residuals", ylab="Alcohol Residuals", col='Darkblue',
     pch=3, size=3)
abline(lm(y ~ x), col='Darkblue', lwd=2)
abline(v = 0, col="red", lty=3)
abline(h = 0, col="red", lty=3)

# Sulphates
y = update(wines.1.red, .~. -sulphates)$res
x = lm(sulphates ~ ., data = wines_reduced[,-c(11)])$res
plot(x, y, xlab="Sulphates Residuals", ylab="Alcohol Residuals", 
     col='Darkblue', pch=3, size=3)
abline(lm(y ~ x), col='Darkblue', lwd=2)
abline(v = 0, col="red", lty=3)
abline(h = 0, col="red", lty=3)
```

As we can see, for every added variable plot, the points are scattered
roughly symmetrically across the best fit line (except for maybe the
chlorides plot). Therefore, the linearity assumption is met for our MLR
model.

**Differences/Similarities in Model A and B**

Model A uses testing and training data sets and uses a greedy algorithm
for model selection based on the lowest BIC and AIC values. Model B uses
testing procedures for model selection. The model selection is done
based on p-values of the predictors through a backward elimination
testing procedure. Both methods ultimately resulted in the same model
-\> model A and model B have the same predictors.

**RESULTS**

```{r}
confint(wines.training_greedy)
```

**Insights:**

All 3 acidity measures (fixed, volatile, citric), sugar, and sulphates are all
positively correlated with alcohol content, whereas chlorides, free $SO_2$, and
density are negatively correlated with alcohol content. Free $SO_2$ in 
particular, seems to have much smaller coefficients (by magnitude), and by 
proxy a weaker correlation, but this could also be due to a choice in units. 
White wines also tend to have lower alcohol contents than red wines.

## CONCLUSION

After fitting various types of linear models to our dataset, we found that 
a full multiple linear regression excluding total sulfur dioxide as a predictor
minimized both training and testing RMSE the best. However, this approach
consistently encountered departures from key model assumptions, particularly 
the normality and constant variance of residuals.

We attempted to address these violations through remedial measures, such
as transformations of the response variable and model adjustments, 
but we were unsuccessful in resolving the assumption failures.
This is a potential limitation in the reliability of our models for
accurately predicting alcohol percentage of new wines. 

One significant contributing factor to this issue was the presence of numerous 
unusual observations in the dataset, which may have introduced noise or
distortions to the modeling process. Addressing this limitation by
exploring alternative models, or reassessing the predictors selected
could improve future outcomes.

Despite these challenges, our systematic approach to model selection,
guided by metrics such as RMSE for prediction accuracy, allowed us to
identify the most optimal model for the task. To our surprise, the
leaps-and-bounds approach, Ridge/LASSO shrinkage, and Principal Components
methods all fell short of the basic greedy model building method. This suggests
that the connection between a wine's alcohol content and chemical indicators
of the wine is fairly simple and straightforward.